Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics

### 2023-03-14 paper/paper.tex
updated to use thyroid

@@

\usepackage{longtable,booktabs}

@@

% Pandoc syntax highlighting

% Pandoc header
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figure-latex/liver-1} \caption{A choropleth map of the smoothed average of liver cancer diagnoses for Australian males. The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average. The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}\label{fig:liver}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figure-latex/liver-hex-1} \caption{A hexagon tile map of the smoothed average of liver cancer diagnoses for Australian males. The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average. The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}\label{fig:liver-hex}
\end{figure}

The choropleth map is an effective spatial display if the size of the geographic units is relatively uniform. This is not the case for most countries. Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips. A choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic {[}\protect\hyperlink{ref-CBATCC}{6}{]}. \emph{Land doesn't get cancer, people do} -- a more effective way to communicate the spatial distributions of cancer statistics is needed.

@@

The hexagon tile map algorithm, automatically matches spatial regions to their nearest hexagon tile, from a grid of tiles. It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas. The algorithm is available in the R package, sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}. Fig. \ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia. Colour maps from substantially below average (blue) to substantially above average (red) rates. The inner city areas have expanded, making it possible to see the cancer incidence in the small, densely populated areas. Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values. It is of interest to know how well the spatial distribution is perceived for this display, in comparison to the choropleth.

@@

The source code to produce this document can be found on \href{https://github.com/srkobakian/experiment/tree/master/paper}{GitHub}.
Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
The full set of images can also be found at: https://github.com/srkobakian/experiment/tree/master/figures/final.

@@

\newpage

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-sugarbag}{}%
1. Kobakian S, Cook D (2019) Sugarbag: Create tessellated hexagon maps.

\leavevmode\hypertarget{ref-atlas}{}%
2. Cancer Council Queensland Australian Cancer Atlas (https://atlas.cancer.org.au).

\leavevmode\hypertarget{ref-GIIV}{}%
3. Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979

\leavevmode\hypertarget{ref-EI}{}%
4. Tufte ER (1990) Envisioning Information. Graphics Press

\leavevmode\hypertarget{ref-BCM}{}%
5. Skowronnek A (2016) Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata. In: Infovis Reading Group WS 2015/16. \url{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}.

\leavevmode\hypertarget{ref-CBATCC}{}%
6. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246

\leavevmode\hypertarget{ref-ACTUC}{}%
7. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260

\leavevmode\hypertarget{ref-NAC}{}%
8. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380

\leavevmode\hypertarget{ref-RSCW}{}%
9. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10

\leavevmode\hypertarget{ref-CDWCS}{}%
10. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224

\leavevmode\hypertarget{ref-review}{}%
11. (2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication.

\leavevmode\hypertarget{ref-BCHLLSW09}{}%
12. Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics. Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383

\leavevmode\hypertarget{ref-GTPCCD}{}%
13. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448

\leavevmode\hypertarget{ref-ggplot2}{}%
14. Wickham H (2009) Ggplot2: Elegant graphics for data analysis. Springer New York

\leavevmode\hypertarget{ref-abs2016}{}%
15. (2018) Australian Statistical Geography Standard (ASGS). Australian Bureau of Statistics

\leavevmode\hypertarget{ref-POG}{}%
16. Matheron G (1963) Principles of geostatistics. Economic Geology 58:1246--1266

\leavevmode\hypertarget{ref-gstat}{}%
17. Gräler B, Pebesma E, Heuvelink G (2016) Spatio-temporal interpolation using gstat. The R Journal 8:204--218

\leavevmode\hypertarget{ref-RCore}{}%
18. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria

\leavevmode\hypertarget{ref-lme4}{}%
19. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48

\leavevmode\hypertarget{ref-taipan}{}%
20. Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis.

\leavevmode\hypertarget{ref-sheets}{}%
21. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.

\leavevmode\hypertarget{ref-figeight}{}%
22. (2019) The essential high-quality data annotation platform. Figure Eight

\leavevmode\hypertarget{ref-rmarkdown}{}%
23. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida

\leavevmode\hypertarget{ref-rticles}{}%
24. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.

\leavevmode\hypertarget{ref-knitr}{}%
25. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research

\leavevmode\hypertarget{ref-tidyverse}{}%
26. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686

\leavevmode\hypertarget{ref-nullabor}{}%
27. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.

\leavevmode\hypertarget{ref-ggthemes}{}%
28. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.

\leavevmode\hypertarget{ref-RColorBrewer}{}%
29. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.

\leavevmode\hypertarget{ref-cowplot}{}%
30. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.

\leavevmode\hypertarget{ref-png}{}%
31. Urbanek S (2013) Png: Read and write png images.

\leavevmode\hypertarget{ref-grid}{}%
32. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria

\leavevmode\hypertarget{ref-kableExtra}{}%
33. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.

>>>>

\usepackage{graphicx}

@@

@@

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\begin{figure}

{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-choro-1}

\caption{A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2. Blue indicates lower than average and red indicates higher than average incidence. A cluster of high incidence is visible on the east coast.}\label{fig:thyroid-choro}
\end{figure}

The choropleth map is an effective spatial display if the size of the geographic units is relatively uniform. This is not the case for most countries. Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips. Fig. \ref{fig:thyroid-choro} shows the choropleth map of thyroid cancer rates in Australia. The choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic {[}\protect\hyperlink{ref-CBATCC}{6}{]}. \emph{Land doesn't get cancer, people do} -- a more effective way to communicate the spatial distributions of cancer statistics is needed.

@@

\begin{figure}

{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-hex-1}

\caption{A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1. The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots.}\label{fig:thyroid-hex}
\end{figure}

The hexagon tile map algorithm, automatically matches spatial regions to their nearest hexagon tile, from a grid of tiles. It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas. The algorithm is available in the R package, sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}. Fig. \ref{fig:thyroid-hex} shows the hexagon tile map. Colour maps from substantially below average (blue) to substantially above average (red) rates. The inner city areas have expanded, making it possible to see the cancer incidence in the small, densely populated areas. Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values. It is of interest to know how well the spatial distribution is perceived for this display, in comparison to the choropleth.

@@

The source code to produce this document can be found on \href{https://github.com/srkobakian/experiment/paper}{GitHub}.
Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
The full set of images can be found here, too.

@@

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-sugarbag}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Kobakian S, Cook D (2019) Sugarbag: Create tessellated hexagon maps. }

\leavevmode\vadjust pre{\hypertarget{ref-atlas}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Cancer Council Queensland {Australian Cancer Atlas (https://atlas.cancer.org.au)}. }

\leavevmode\vadjust pre{\hypertarget{ref-GIIV}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979}

\leavevmode\vadjust pre{\hypertarget{ref-EI}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Tufte ER (1990) {Envisioning Information}. Graphics Press}

\leavevmode\vadjust pre{\hypertarget{ref-BCM}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Skowronnek A (2016) {Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata}. In: {Infovis Reading Group WS 2015/16}. \href{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}{https://alsino.io/static/papers/BeyondChoropleths\_AlsinoSkowronnek.pdf. }}

\leavevmode\vadjust pre{\hypertarget{ref-CBATCC}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Kocmoud C, House D (1998) {A Constraint-based Approach to Constructing Continuous Cartograms}. In: Proc. Symp. Spatial data handling. pp 236--246}

\leavevmode\vadjust pre{\hypertarget{ref-ACTUC}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Dorling D (2011) \href{https://doi.org/10.1002/9780470979587.ch33}{{Area Cartograms: Their Use and Creation}}. In: Concepts and techniques in modern geography (CATMOG). pp 252--260}

\leavevmode\vadjust pre{\hypertarget{ref-NAC}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Olson JM (1976) \href{https://doi.org/10.1111/j.0033-0124.1976.00371.x}{{Noncontiguous Area Cartograms}}. The Professional Geographer 28:371--380}

\leavevmode\vadjust pre{\hypertarget{ref-RSCW}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Raisz E (1963) \href{https://doi.org/10.1080/00221343608987880}{{Rectangular Statistical Cartograms of the World}}. Journal of Geography 35:8--10}

\leavevmode\vadjust pre{\hypertarget{ref-CDWCS}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Monmonier M (2005) \href{https://doi.org/10.1191/0309132505ph540pr}{{Cartography: Distortions, World-views and Creative Solutions}}. Progress in Human Geography 29:217--224}

\leavevmode\vadjust pre{\hypertarget{ref-review}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{(2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication. }

\leavevmode\vadjust pre{\hypertarget{ref-BCHLLSW09}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics. Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383}

\leavevmode\vadjust pre{\hypertarget{ref-GTPCCD}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448}

\leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{Wickham H (2009) \href{http://had.co.nz/ggplot2/book}{ggplot2: Elegant graphics for data analysis}. Springer New York}

\leavevmode\vadjust pre{\hypertarget{ref-abs2016}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{(2018) \href{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}{{Australian Statistical Geography Standard (ASGS)}}. Australian Bureau of Statistics }

\leavevmode\vadjust pre{\hypertarget{ref-POG}{}}%
\CSLLeftMargin{16. }%
\CSLRightInline{Matheron G (1963) \href{http://dx.doi.org/10.2113/gsecongeo.58.8.1246}{Principles of geostatistics}. Economic Geology 58:1246--1266}

\leavevmode\vadjust pre{\hypertarget{ref-gstat}{}}%
\CSLLeftMargin{17. }%
\CSLRightInline{Gräler B, Pebesma E, Heuvelink G (2016) \href{https://journal.r-project.org/archive/2016/RJ-2016-014/index.html}{Spatio-temporal interpolation using gstat}. The R Journal 8:204--218}

\leavevmode\vadjust pre{\hypertarget{ref-RCore}{}}%
\CSLLeftMargin{18. }%
\CSLRightInline{R Core Team (2019) \href{https://www.R-project.org/}{R: A language and environment for statistical computing}. R Foundation for Statistical Computing, Vienna, Austria}

\leavevmode\vadjust pre{\hypertarget{ref-lme4}{}}%
\CSLLeftMargin{19. }%
\CSLRightInline{Bates D, Mächler M, Bolker B, Walker S (2015) \href{https://doi.org/10.18637/jss.v067.i01}{Fitting linear mixed-effects models using {lme4}}. Journal of Statistical Software 67:1--48}

\leavevmode\vadjust pre{\hypertarget{ref-taipan}{}}%
\CSLLeftMargin{20. }%
\CSLRightInline{Kobakian S, O'Hara-Wild M (2018) \href{https://CRAN.R-project.org/package=taipan}{Taipan: Tool for annotating images in preparation for analysis}. }

\leavevmode\vadjust pre{\hypertarget{ref-sheets}{}}%
\CSLLeftMargin{21. }%
\CSLRightInline{Bryan J, Zhao J (2018) \href{https://CRAN.R-project.org/package=googlesheets}{Googlesheets: Manage google spreadsheets from r}. }

\leavevmode\vadjust pre{\hypertarget{ref-figeight}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{(2019) \href{https://www.figure-eight.com/}{The essential high-quality data annotation platform}. Figure Eight }

\leavevmode\vadjust pre{\hypertarget{ref-rmarkdown}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Xie Y, Allaire JJ, Grolemund G (2018) \href{https://bookdown.org/yihui/rmarkdown}{R markdown: The definitive guide}. Chapman; Hall/CRC, Boca Raton, Florida}

\leavevmode\vadjust pre{\hypertarget{ref-rticles}{}}%
\CSLLeftMargin{24. }%
\CSLRightInline{Allaire J, Xie Y, R Foundation, et al (2019) \href{https://CRAN.R-project.org/package=rticles}{Rticles: Article formats for r markdown}. }

\leavevmode\vadjust pre{\hypertarget{ref-knitr}{}}%
\CSLLeftMargin{25. }%
\CSLRightInline{Xie Y (2014) \href{http://www.crcpress.com/product/isbn/9781466561595}{Knitr: A comprehensive tool for reproducible research in {R}}. Implementing reproducible computational research }

\leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Wickham H, Averick M, Bryan J, et al (2019) \href{https://doi.org/10.21105/joss.01686}{Welcome to the {tidyverse}}. Journal of Open Source Software 4:1686}

\leavevmode\vadjust pre{\hypertarget{ref-nullabor}{}}%
\CSLLeftMargin{27. }%
\CSLRightInline{Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) \href{https://CRAN.R-project.org/package=nullabor}{Nullabor: Tools for graphical inference}. }

\leavevmode\vadjust pre{\hypertarget{ref-ggthemes}{}}%
\CSLLeftMargin{28. }%
\CSLRightInline{Arnold JB (2019) \href{https://CRAN.R-project.org/package=ggthemes}{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. }

\leavevmode\vadjust pre{\hypertarget{ref-RColorBrewer}{}}%
\CSLLeftMargin{29. }%
\CSLRightInline{Neuwirth E (2014) \href{https://CRAN.R-project.org/package=RColorBrewer}{RColorBrewer: ColorBrewer palettes}. }

\leavevmode\vadjust pre{\hypertarget{ref-cowplot}{}}%
\CSLLeftMargin{30. }%
\CSLRightInline{Wilke CO (2019) \href{https://CRAN.R-project.org/package=cowplot}{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. }

\leavevmode\vadjust pre{\hypertarget{ref-png}{}}%
\CSLLeftMargin{31. }%
\CSLRightInline{Urbanek S (2013) \href{https://CRAN.R-project.org/package=png}{Png: Read and write PNG images}. }

\leavevmode\vadjust pre{\hypertarget{ref-grid}{}}%
\CSLLeftMargin{32. }%
\CSLRightInline{R Core Team (2019) \href{https://www.R-project.org/}{R: A language and environment for statistical computing}. R Foundation for Statistical Computing, Vienna, Austria}

\leavevmode\vadjust pre{\hypertarget{ref-kableExtra}{}}%
\CSLLeftMargin{33. }%
\CSLRightInline{Zhu H (2019) \href{https://CRAN.R-project.org/package=kableExtra}{kableExtra: Construct complex table with 'kable' and pipe syntax}. }

\end{CSLReferences}
